---
title: "SomePlots"
author: "Lance Wrobel"
date: "October 17, 2018"
output: html_document
---
This is a notebook of me playing around with the data a little bit, a work in progress.

First download apartment-electrical.tar.gz and apartment-weather.tar.gz from http://traces.cs.umass.edu/index.php/Smart/Smart into workspace. Uncomment 
(remove pound signs) to run below code chunk. Adjust file paths for your computer.
```{r}
library(readr)
library(plyr)
#untar("apartment-electrical.tar.gz",list=TRUE)  ## check contents
#untar("apartment-electrical.tar.gz")
#untar("apartment-weather.tar.gz",list=TRUE)  ## check contents
#untar("apartment-weather.tar.gz")
#apartment9_electical_2014 <- read_csv("../../apartment/2014/Apt9_2014.csv",header = FALSE)
#colnames(apartment9_electical_2014) = c("time","Power kW")
#apartment_weather_2014 <- read_csv("../../apartment-weather/apartment2014.csv")

filenames = list.files(path = "C:\\Users\\lance\\Documents\\R\\win-library\\3.4\\AMATHProj\\apartment\\2014", pattern="*.csv")
setwd("C:\\Users\\lance\\Documents\\R\\win-library\\3.4\\AMATHProj\\apartment\\2014")

#all_dfs = lapply(filenames, read_csv,col_names = c("time","Power kW")) #old code, keep commented

read_csv_filename <- function(filename){
    ret <- read_csv(filename,col_names = c("time","Power kW"))
    m = nchar(filename)
    ret$apartment <- substr(filename,1,m-4) #preserve apartment name
    return(ret)
}

big_electrical_df_2014 <- ldply(filenames, read_csv_filename)

setwd("C:\\Users\\lance\\Documents\\R\\win-library\\3.4\\AMATHProj")
```


First clean the data somewhat.
```{r}
library(tidyr)
library(dplyr)
library(ggplot2)
library(lubridate)

big_electrical_df_2014_clean<-big_electrical_df_2014 %>% separate(time,c("date","time"),' ') %>%
  separate(date,c("year","month","date"),"-") %>% separate(time,c("hour","minute","second"),":")

apartment_weather_2014_clean <- apartment_weather_2014 
apartment_weather_2014_clean$time<-as_datetime(apartment_weather_2014_clean$time) #time is hourly

apartment_weather_2014_clean <- apartment_weather_2014 
apartment_weather_2014_clean$time<-as_datetime(apartment_weather_2014_clean$time) #time is hourly

apartment_weather_2014_clean <-apartment_weather_2014_clean %>% separate(time,c("date","time"),' ') %>%
  separate(date,c("year","month","date"),"-") %>% separate(time,c("hour","minute","second"),":")

```
Plot energy consumption over months
```{r}

#plot energy consumption by different months
temp_1 = aggregate(list(`Power kW`=big_electrical_df_2014_clean$`Power kW`),list(month =factor(big_electrical_df_2014_clean$month)),mean) 

ggplot(temp_1, aes(month,Power.kW,na.rm=TRUE))+
         geom_bar(stat="identity")+theme(axis.text.x=element_text(angle=60,hjust=1))+ggtitle("Average energy consumption per month")

```

Plot average energy consumption for each hour of the day
```{r}
#plot energy consumption over course of 24 hour day
temp_1 = aggregate(list(`Power kW`=big_electrical_df_2014_clean$`Power kW`),list(hour =factor(big_electrical_df_2014_clean$hour)),mean) 

ggplot(temp_1, aes(hour,Power.kW,na.rm=TRUE))+
         geom_bar(stat="identity")+theme(axis.text.x=element_text(angle=60,hjust=1))+ggtitle("Average energy consumption per hour")
```
A weather data plot for average temperature per month
```{r}
temp = aggregate(list(temperature=apartment_weather_2014_clean$temperature),list(month =factor(apartment_weather_2014_clean$month)),mean) 
ggplot(temp, aes(x=month,y=temperature,na.rm=TRUE))+
  geom_bar(stat="identity")+ggtitle("Average Temperature per month")
```

